SafeStreets is a crowd-sourced application that intends to provide users with the possibility to notify authorities when traffic violations occur, and in particular parking violations. The application allows users to send pictures of violations, including their date, time, and position, to authorities. Examples of violations are vehicles parked in the middle of bike lanes or in places reserved for people with disabilities, double parking, and so on.

SafeStreets stores the violation reports provided by users, that can be made from the official mobile application or from the SafeStreets website, so that users and authorities can visualize and analyze the data received by the system, for example by highlighting the streets (or the areas) with the highest frequency of violations, or the vehicles that commit the most violations. The data can be accessed with different levels of visibility, where most sensitive data can only be mined by authorities.

SafeStreets also provide a service aimed at helping municipalities to identify potentially unsafe areas and suggest possible interventions. To improve the accuracy of these features, a municipality can also offer a service for retrieving info about accidents in their territory, so that SafeStreets is able to cross the municipality's data with its own stored data and also analyze and suggest possible improvements to the areas with most reports.
\subsubsection{Goals}
\begin{enumerate}[label={G\arabic*.}]
    \myitem {Report certified traffic violations to authorities of city where the violations have happened.} \label{G_report_auth}
    \myitem {Store data about violations and cross it with municipality's one when an API to its data is provided.} \label{G_store_cross_data}
    \myitem {Allow municipalities to generate a list of possible reasonable interventions to resolve the violations detected in most unsafe areas.} \label{G_interventions}
    \myitem {Recognize public institution officers automatically during registration to setup correctly accounts of municipalities and authorities.} \label{G_inst_registration}
    \myitem {Provide a synthesis of all the violations' data to users, based on their authorization level.} \label{G_visualization}
    \begin{enumerate}[label={G\arabic{enumi}.\arabic*.}]
    	\myitem {Normal users can access only to aggregated data, without seeing any private info about a reported violation, like the license plate or the personal info of the user who reported the violation.} \label{G_visualization_cit}
    	\myitem {Authenticated authorities can access to all violations' data, as aggregated data or singular reports.} \label{G_visualization_auth}
    \end{enumerate}
	\myitem {Allow users to send a report of a possible traffic violation, identifying clearly the transgressor.} \label{G_accept_reports}
	\myitem {Allow users to check their personal info and the list of violations they reported.} \label{G_check_info}
\end{enumerate}
