In this section project requirements are presented and relationships between goals, domain assumptions and requirements are clearly stated, to provide a logical representation of the model analysis.

\bigskip
Requirements:
\begin{enumerate}[label={R\arabic*.}]
	\myitem {When a traffic violation is reported, the report supervisor has to verify it and then notify the authorities.} \label{R_supervisor}
	\myitem {Reports about traffic violations need to be stored in a database, also associating them to the user profile who sent them.} \label{R_storing_report}
	\myitem {The system needs to integrate reported traffic violations with data from the municipality and analyse all the data with an algorithm to find possible interventions to address the detected main cause of the violations.} \label{R_mun_integration}
	\myitem {The suggestions about interventions must be sent to the municipality to evaluate a possible solution.} \label{R_mun_intervention_send}
	\myitem {Traffic violations data must be available for public consultation with different levels of visibility, according to user's level of authorisation.} \label{R_data_vis}
	\begin{enumerate}[label={R\arabic{enumi}.\arabic*.}]
		\myitem {The system should allow a normal user to access only to aggregated data, without the license plate of the reported vehicle or the personal info of the user who reported the violation.} \label{R_data_vis_cit}
		\myitem {The system should allow the authorities to access the data without any limitation.} \label{R_data_vis_auth}
	\end{enumerate}
	\myitem {The system must ascertain the identity of a public institution that want to register to the system from its PCE, completing the account with the necessary data.} \label{R_institution_certification}
	\myitem {The system must receive correctly reports about the various traffic violations from the users.} \label{R_report_reception}
	\myitem {A violation report must have a photo attached that clearly shows the license plate and the type of violation.} \label{R_photo} 
\end{enumerate}

\bigskip
\bigskip
Goal Logical Derivation:
\begin{enumerate}[label={}]
	\item \myref{G_report_auth}
	\begin{itemize}[label={}]
		\item \myref{R_supervisor}
		\item \myref{R_report_reception}
		\item \myref{D_reports}
		\item \myref{D_supervisor}
		\item \myref{D_city_auth}
	\end{itemize}
	\item \myref{G_interventions}
	\begin{itemize}[label={}]
		\item \myref{R_storing_report}
	 	\item \myref{R_mun_integration}
	 	\item \myref{R_mun_intervention_send}
	 	\item \myref{D_mun_availability}
	 	\item \myref{D_mun_accuracy}
	 	\item \myref{D_pce}
	\end{itemize}
	\item \myref{G_inst_registration}
	\begin{itemize}[label={}]
		\item \myref{R_institution_certification}
		\item \myref{D_pce}
		\item \myref{D_pce_api}
	\end{itemize}
	\item \myref{G_visualization}
	\begin{itemize}[label={}]
		\item \myref{R_data_vis}
		\item \myref{D_internet}
	\end{itemize}

	\item \myref{G_visualization_cit}
	\begin{itemize}[label={}]
		\item \myref{R_data_vis_cit}
	\end{itemize}
	\item \myref{G_visualization_auth}
	\begin{itemize}[label={}]
		\item \myref{R_data_vis_auth}
	\end{itemize}

	\item \myref{G_accept_reports}
	\begin{itemize}[label={}]
		\item \myref{R_report_reception}
		\item \myref{R_photo}
		\item \myref{D_gps}
		\item \myref{D_internet}
	\end{itemize}
	\item \myref{G_check_info}
	\begin{itemize}[label={}]
		\item \myref{R_storing_report}
		\item \myref{D_internet}
	\end{itemize} 
\end{enumerate}

\bigskip
Traceability matrix:


Login use case is omitted for simplicity, because it would be used in almost every requirement.


\begin{tabular}{|l|>{\raggedright\arraybackslash}p{8cm}|}
	\hline 
	Requirements & Use cases \\ 
	\hline 
	R1 &  \\ 
	\hline 
	R2 &  NotifyViolations\\ 
	\hline 
	R3 &  \\ 
	\hline 
	R4 &  \\ 
	\hline 
	R5 & AnalyzeData \\ 
	\hline 
	R5.1& AnalyzeData-citizen \\ 
	\hline 
	R5.2& AnalyzeData-authority \\ 
	\hline 
	R6 & Registration-authority \\ 
	\hline 
	R7 & NotifyViolations \\ 
	\hline 
	R8 & NotifyViolations \\ 
	\hline 
\end{tabular} 
